% MIT/X Consortium License
% © 2024 - 2025 Mahmoud Elshimi <mahmoudelshimi@protonmail.ch>
\documentclass[letterpaper, 10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage[colorlinks=true,urlcolor=black]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

\author{}
\date{}

\title{\Huge \textbf{Mahmoud ElShimi}}
\begin{document}
\maketitle

\noindent
Email: \href{mailto:mahmoudelshimi@protonmail.ch}{mahmoudelshimi@protonmail.ch} \hfill
WhatsApp: \href{https://wa.me/201003123253?text=Hey,\%20I\%20came\%20from\%20your%20CV}{+201003123253 \hspace{2.4cm}} \\
GitHub: \href{https://github.com/mahmoudelshimi}{github.com/mahmoudelshimi} \hfill
LinkedIn: \href{https://www.linkedin.com/in/mahmoudelshimi}{linkedin.com/in/mahmoudelshimi}

\section*{Professional Summary}
Junior Backend Python Developer with expertise in DevOps principles, cloud deployment, and Linux system administration. Experienced in deploying and maintaining ERP solutions with Odoo and developing web applications using Django in cloud environments. Skilled in Linux systems, scripting, and infrastructure automation, with a focus on performance and scalability. Currently seeking a new role in Backend Development or DevOps to leverage my skills in infrastructure optimization and automation while contributing to innovative projects.

\section*{Work Experience}
\noindent\textbf{Backend Python Developer}\\
\textit{Perfect Solution} \hfill \textit{July 2024 - Present}
\begin{itemize}[leftmargin=*]
    \item Designed and deployed Odoo ERP solutions in linux \& cloud environments, ensuring high availability and scalability.
    \item Customized Odoo modules to align with business needs and improve operational efficiency.
    \item Automated deployment workflows to streamline delivery and minimize downtime.
    \item Monitored and maintained Linux servers, ensuring optimal performance and security compliance.
    \item Configured and managed cloud infrastructure, optimizing resource utilization and security.
    \item Worked collaboratively with cross-functional teams to implement containerized solutions using Docker.
\end{itemize}

\noindent\textbf{IT Technical Support}\\
\textit{Ideal Systems Company} \hfill \textit{January 2024 - June 2024}
\begin{itemize}[leftmargin=*]
    \item Resolved ERP software issues, providing technical support to enhance client satisfaction.
    \item Installed and managed software systems, leveraging Linux expertise for efficient troubleshooting.
    \item Utilized Microsoft SQL Server and Crystal Reports for application management and reporting.
\end{itemize}

\noindent\textbf{DSL Technical Support}\\
\textit{Orange Egypt} \hfill \textit{February 2023 - January 2024}
\begin{itemize}[leftmargin=*]
    \item Configured static IPs, port forwarding, and CPEs to meet client requirements.
    \item Diagnosed connectivity issues using company tools and resolved complex technical problems.
    \item Provided technical support for networking and Linux-based systems.
\end{itemize}
\newpage

\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{DevOps \& Cloud}: Expertise in CI/CD pipelines, containerization (Docker), \& cloud infrastructure (AWS).
    \item \textbf{Linux \& Unix Systems Administration}: Expertise in Debian, Red Hat, and OpenBSD for server management and network configuration.
    \item \textbf{Automation and Scripting}: Skilled in Bash to automate tasks and optimize system performance.
    \item \textbf{Backend Development}: Developing secure web applications with Django.
    \item \textbf{Networking}: Proficient in TCP/IP, DNS, DHCP, VLANs, VPNs, and firewall configurations.
    \item \textbf{Database Management}: Hands-on experience with PostgreSQL for efficient data handling and backups.
    \item \textbf{Version Control}: Proficient with Git and GitHub for code management and collaboration.
    \item \textbf{Programming Languages}: Expertise in Python and C for software development.
    \item \textbf{Mathematics}: Applied skills in Calculus and Linear Algebra for technical problem-solving.
    \item \textbf{Problem-Solving and Soft Skills}: Excellent analytical abilities, communication, and teamwork skills.
\end{itemize}

\section*{Certifications}
\begin{itemize}[leftmargin=*]
 \item \textbf{Oracle Cloud Infrastructure 2024 Foundations Associate} \hfill \textit{2025}
 \item \textbf{Oracle Cloud Infrastructure 2024 Certified AI Foundations Associate} \hfill \textit{2025}
 \item \textbf{Oracle Cloud Infrastructure 2024 Data Certified Foundations Associate} \hfill \textit{2025}
\end{itemize}


\section*{Projects}

\noindent\textbf{\href{https://github.com/mahmoudElshimi/psi_letter_of_guarantee}{Psi Letter of Guarantee Odoo Module}} \hfill \textit{2025} \\
Developed an Odoo module to manage letters of guarantee with features including:
\begin{itemize}[leftmargin=*]
    \item Integration with partners and banks for seamless guarantee tracking.
    \item Comprehensive reporting for financial insights and auditing.
\end{itemize}
\vspace{0.2cm}

\noindent\textbf{\href{https://rusetta.openbsd.amsterdam/platform_philosophy/}{Rusetta (rusetta.openbsd.amsterdam/platform\_philosophy)}}   \hfill \textit{2024} \\
Developed an educational platform using Django with the following key features:
\begin{itemize}[leftmargin=*]
    \item A dashboard for teachers' assistants to manage students, information, news, subscriptions, and tests.
    \item Enhanced video protection mechanisms to prevent unauthorized downloads.
    \item Detailed logging of all actions performed by assistants for monitoring and auditing purposes.
\end{itemize}

\vspace{0.2cm}

\noindent\textbf{\href{https://github.com/mahmoudElshimi/rusetta_assist}{Rusetta Assist Odoo Module}} \hfill \textit{2024} \\
Developed an Odoo module for student management with features including:
\begin{itemize}[leftmargin=*]
    \item Recording student attendance, exam records, and marks.
    \item Managing exams and assigning marks with advanced filtering options.
\end{itemize}

\section*{Education}
\vspace{-0.3cm}
\noindent{Bachelor Degree from Al-Azhar University, Cairo.}\hfill \textit{2024} 
\vspace{0.5cm}

\noindent \textbf{References available upon request,} \href{https://raw.githubusercontent.com/mahmoudElshimi/resume/main/mahmoud_elshimi_resume.pdf}{Latest resume available here}.


\end{document}

